Modelling and Optimization of Injector Parameters with OpenFOAM and Globalizer Tools

### 2021-07-05 2021/ICNAAM/2021_ICNAAM.tex
Update references

The calculations were performed on the computer cluster of the Institute for Systems Programming and the UniHub web-lab. The web-lab architecture is based on the cloud computing model where resources (servers, networks, storage systems, applications, etc.) are provided remotely as a set of different-level services with on-demand servicing.

@@

The fluid dynamics for the problem described in this paper is defined by the Navier-Stokes equations for an incompressible fluid:
\[
\nabla \cdot \vec{U} = 0,
\]
\[
\frac{\partial \vec{U}}{\partial t} + \nabla \cdot \left( \vec{U} \otimes \vec{U}\right) - \nabla \cdot v \left( \nabla \vec{U} + (\nabla \vec{U})^T\right) = - \frac{1}{\rho} \nabla p,
\]
where $\vec{U}$ is the velocity vector, $v$  is the liquid viscosity (assumed constant), $p$  is the overpressure, $\rho$ is the density of the liquid. In this system of equations, there are two unknown variables: $\vec{U}$  and $p$. For each of these variables, initial conditions are set: 
\[
\vec{U}(x,y) = 0, \; p(x,y) = 0.
\]
There are three types of boundaries in the computational domain; special boundary conditions are set on each of them. 
On a rigid wall:
\[
\nabla p \cdot \vec{n} = 0, \; \vec{U} = 0.
\]
At the entrance to the computational domain:
\[
\nabla p \cdot \vec{n} = 0, \; \vec{U} = \vec{U_i}.
\]
At the exit of the computational domain:
\[
 p = 0, \; \vec{U} = \vec{U_o}.
\]

@@

The calculation was carried out with the standard pisoFoam solver and the PISO algorithm \cite{Issa1986_2}.
A total of 300 finite elements were involved in the calculation. The process of finding the effective channel thickness took 3395 seconds on an Intel(R) Xeon(R) CPU X5670 2.93 GHz, during which time 69 iterations of the global search algorithm were performed. The horizontal component of the velocity at the entrance to the computational domain $\vec{U_i}$  was 10 m/s. The pressure at the exit of the computational domain $p_o$ was equal to zero, just like all components of the velocity vector at the exit $\vec{U_o}$ . Linear dimensions of the computational domain are shown in the schematic of Figure 1. As a result of solving the problem, the optimum channel thickness (0.59 cm) was found, giving the minimum fuel consumption.

@@

\cite{Issa1986_1}

>>>>

The calculations were performed on the computer cluster of the Institute for Systems Programming and the UniHub web-lab \cite{UniHub}. The web-lab architecture is based on the cloud computing model where resources (servers, networks, storage systems, applications, etc.) are provided remotely as a set of different-level services with on-demand servicing.

@@

The fluid dynamics for the problem described in this paper is defined by the Navier-Stokes equations for an incompressible fluid:
\[
\nabla \cdot \vec{U} = 0,
\]
\[
\frac{\partial \vec{U}}{\partial t} + \nabla \cdot \left( \vec{U} \otimes \vec{U}\right) - \nabla \cdot v \left( \nabla \vec{U} + (\nabla \vec{U})^T\right) = - \frac{1}{\rho} \nabla p,
\]
where $\vec{U}$ is the velocity vector, $v$  is the liquid viscosity (assumed constant), $p$  is the overpressure, $\rho$ is the density of the liquid. In this system of equations, there are two unknown variables: $\vec{U}$  and $p$. For each of these variables, initial conditions are set: 
\[
\vec{U}(x,y) = 0,
\]
\[
p(x,y) = 0.
\]
There are three types of boundaries in the computational domain; special boundary conditions are set on each of them. 
On a rigid wall:
\[
\nabla p \cdot \vec{n} = 0,
\]
\[
\vec{U} = 0.
\]
At the entrance to the computational domain:
\[
\nabla p \cdot \vec{n} = 0,
\]
\[
\vec{U} = \vec{U_i}.
\]
At the exit of the computational domain:
\[
 p = 0,
\]
\[
\vec{U} = \vec{U_o}.
\]

@@

The calculation was carried out with the standard pisoFoam solver and the PISO algorithm \cite{Issa1986_2,Issa1986_1}.
A total of 300 finite elements were involved in the calculation. The process of finding the effective channel thickness took 3395 seconds on an Intel(R) Xeon(R) CPU X5670 2.93 GHz, during which time 69 iterations of the global search algorithm were performed. The horizontal component of the velocity at the entrance to the computational domain $\vec{U_i}$  was 10 m/s. The pressure at the exit of the computational domain $p_o$ was equal to zero, just like all components of the velocity vector at the exit $\vec{U_o}$ . Linear dimensions of the computational domain are shown in the schematic of Figure 1. As a result of solving the problem, the optimum channel thickness (0.59 cm) was found, giving the minimum fuel consumption.

@@
